### 2020-12-02 paper/sections/design.tex
first draft

Without loss of generality, we denote the object detection service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input video chunk $ x_i $. It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each input video chunk $ x \in X_{\rm ref} $ using \emph{reference configuration} (the most expensive configuration). We use this $ \vec{y}_{\rm ref} $ as the ground truth label. For each video chunk $ x_c $ that uses a configuration $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the F1 score as the accuracy $ \mathcal{A} $, which is the harmonic mean of precision and recall, consistent with prior work~\cite{jiang2018chameleon,kang2017f1_noscope,zhang2017f1_live}. Besides, to compute the accuracy of a frame that was not sampled by $ c $, we use the location of objects from the previous sampled frame.

@@

In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{Section: experiment}. We denote the \emph{action-value function} as $ Q(s, c; \theta) $ and the optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(s, c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over state  $ s $ and the configuration $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

@@

In our solution, the agent is trained by the reward feedback. In the above formulation, we define resource consumption rate $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at configuration $ c $. Basically, we want the agent to choose a proper configuration for minimizing the resource consumption while remaining acceptable accuracy. Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the resource consumption ratio $ \Delta s $. We introduce a linear factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

>>>>

To automaticly choose different configuration for video stream, we divides the video into T-second intervals as video chunks, and profiles configurations for each video chunk. Without loss of generality, we denote the object detection service as $ \vec{y}_i = M(x_i) $ that provides a predicted result list $ \vec{y}_i $ for each input video chunk $ x_i $. It has a baseline output $ \vec{y}_{\rm ref} = M(x_{\rm ref}) $ for each input video chunk $ x \in X_{\rm ref} $ using \emph{reference configuration} (the most expensive configuration). We use this $ \vec{y}_{\rm ref} $ as the ground truth label. For each video chunk $ x_c $ that uses a configuration $ c $, the output $ \vec{y}_c = M(x_c) $. Therefore, we have an accuracy metric $ \mathcal{A}_c $ by comparing $ \vec{y}_{\rm ref} $ and $ \vec{y}_c $. In general, we use the F1 score as the accuracy $ \mathcal{A} $, which is the harmonic mean of precision and recall, consistent with prior work~\cite{jiang2018chameleon,kang2017f1_noscope,zhang2017f1_live}. Besides, to compute the accuracy of a frame that was not sampled by $ c $, we use the location of objects from the previous sampled frame.

@@

In our system, we define 48 discrete actions to indicate 48 configuration, and the specific configurations are provided in Section~\ref{subsec: configuration}. We denote the \emph{action-value function} as $ Q(s, c; \theta) $ and the optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(s, c; \theta) $ where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over state  $ s $ and the configuration $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

@@

In our solution, the agent is trained by the reward feedback. In the above formulation, we define resource consumption rate $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $ at configuration $ c $. Basically, we want the agent to choose a proper configuration for minimizing the resource consumption while remaining acceptable accuracy. Therefore the overall reward $ r $ should be positively correlated with the accuracy $ \mathcal{A} $ while negatively with the resource consumption ratio $ \Delta s $. We introduce a balance factor $ \beta $ to form a linear combination $ r = \beta \mathcal{A} - (1-\beta) \Delta s  $ as the \emph{reward function} $ R(\Delta s, \mathcal{A}) $. %% \\

### 2020-12-02 paper/sections/experiment.tex
first draft

\section{Experiment}
\label{Section: experiment}

\subsection{Experiment Setup}
\textbf{Datasets:} Due to most of public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution, while others can guarantee resolution but cannot provide sufficient frame rate, but in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows. First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd"). Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes. In addition, these videos need to be as dynamic as the real world, such as not standing still for too long. Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy. For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score \textcolor{note}{this may need to be modified, chen tang}.

Based on the above filtering strategy, we finally selected three datasets:

M6: The M6 is the longest motorway in Britain and the most important road from the Midlands to the West Coast. Thousands of cars travel on it every day. This video was taken from a traffic camera, and its natural dynamics allows us to experiment with this video.

Duke: Duke is a video from a fixed camera placed at an intersection. Because it is fixed in the middle of the intersection, the traffic flow in the video increases or decreases periodically as the traffic light change.

Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.
\subsection{Some results}

@@

\begin{figure*}[!t]
		\begin{minipage}[t]{0.32\linewidth}
			\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
			\centerline{(a) M6}
		\end{minipage}
		\hfill
		\begin{minipage}[t]{0.32\linewidth}
			\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
			\centerline{(b) Duke}
		\end{minipage}
		\hfill
		\begin{minipage}[t]{0.32\linewidth}
			\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
			\centerline{(c) Multi Camera Dataset}
		\end{minipage}		
		\caption{The effect of different models, frame rate, and resolutions on accuracy and processing time. AutoConfigure (blue) consistently outperforms the baseline of one-time update (magenta) across different datasets. Each dot represents the results of running each solution.}
		\label{fig_results}
\end{figure*}

>>>>

\section{Evaluation}
\label{Section: experiment}

\subsection{Dataset and Metric}
\label{subsec: datasets}

Most public sources datasets cannot fully satisfy all configuration choices, for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution. In contrast, others can ensure resolution but cannot provide a sufficient frame rate. Still, in recent years, most of the driving recorder can provide enough resolution and frame rate, so we try to use Youtube video as fellows. We selected three datasets: M6, Duke, and Multi-Camera Dataset. M6 was taken from a traffic camera on the longest motorway in Britain. Duke is a video from a fixed camera placed at an intersection, and  the traffic flow in the video increases or decreases periodically as the traffic light change. Since the first two datasets were sourced from a fixed camera, to ensure that AutoConfigure still performs better when road conditions change dramatically, we used three videos collected from the dashcam. We combined them into one video, Multi-Camera Dataset.

For metric, we use the F1 score as the accuracy and average GPU processing time per frame as the resource consumption, detail described in Section \ref{subsec: formulation}.
%First, in order to eliminate the bias caused by Cookies and personal preferences, we use private browsing mode to search keywords (e.g., "drivecam highway hd"). Second, manually delete irrelevant videos (e.g., ads for some driving recorders) and download videos that are longer than ten minutes. In addition, these videos need to be as dynamic as the real world, such as not standing still for too long. Becaues of none of these videos contained ground truth, we used the data of the original video output from DNN as the tags to calculate the accuracy. For instance, in object detection, the accuracy is defined by the F1 score with respect to the server-side DNN output in highest resolution (original) with over 50$\%$ confidence score.Based on the above filtering strategy, we finally selected three datasets:

%we selected three datasets:
%M6: The M6 is the longest motorway in Britain and the most important road from the Midlands to the West Coast. Thousands of cars travel on it every day. This video was taken from a traffic camera, and its natural dynamics allows us to experiment with this video.
%
%Duke: Duke is a video from a fixed camera placed at an intersection. Because it is fixed in the middle of the intersection, the traffic flow in the video increases or decreases periodically as the traffic light change.
%
%Mutli Camera Dataset: Since the first two datasets were sourced from a fixed camera, in order to ensure that AutoConfigure still has better performance when road conditions change dramatically, we used three videos collected from the dashcam, and since they are relatively similar, we combined them into one video.

\begin{figure*}[!t]
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/m6.pdf}}
		\centerline{(a) M6}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/duke.pdf}}
		\centerline{(b) Duke}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=6.5cm]{figures/_Westbound_Eastbound_Rear.pdf}}
		\centerline{(c) Multi-Camera Dataset}
	\end{minipage}		
	\caption{AutoConfigure (blue) consistently outperforms the baseline of one-time profiling (magenta) across different datasets. Each dot represents the results of running each solution.}
	\label{fig: results}
\end{figure*}

\subsection{Configuration Selection}
\label{subsec: configuration}
We simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.

\subsection{Experiment Parameters}
We apply a deep Q-learning network policy to train the agent. In the training procedure, we build up to eight independently identical environments for each data set to speed up the training and decrease the data's dependency. The leaning rate is set to 0.001. For each dataset, we train the agent 10 epochs and 1000 steps per epoch. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

\begin{table}[!t]
	\centering
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\resizebox{0.4\textwidth}{!}{
		\begin{tabular}{cccccc}
			\toprule
			Notation          & Value & & & Notation     & Value  \\ \midrule
			$\epsilon$    & 0.8    & & & $k_1$      & 3   \\
			$\gamma$      & 0.9  & & & $k_2$    & 3    \\
			$ \beta $ & 0.2,0.3,...,0.9 & & & $ T (train) $ & 1  \\
			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
	\end{tabular}}
	\caption{Experiment parameter}
	\label{tab: parameters}
	%	\vspace{-0.5cm}
\end{table}

\subsection{Experiment Results}
We evaluate AutoConfigure on M6, Duke, and Multi-Camera Dataset video streams. Figure \ref{fig: results} shows that AutoConfigure consistently outperforms the baseline of static configuration (profiling configurations once at the beginning of a video stream) along with resource consumption and several accuracy metrics on different datasets. Each magenta dot represents one static configuration solution. These static configuration solutions including some expensive configurations, such as \{FasterRCNN+InceptionResNetV2, 640p, 30fps\}, \{FasterRCNN+ResNet50V1, 1024p, 25fps\}, and some cheap configurations, such as \{SSD+ResNet152V1, 640p, 1fps\}, \{SSD+ResNet152V1, 640p, 2fps\}, \{SSD+ResNet152V1, 640p, 5fps\}. Each blue dot represents one AutoConfigure configuration solution, which is dependent on the balance factor $\beta$ in reward function, presented in Section \ref{subsec: reward}. The detailed discussion about differents AutoConfigure solutions is in Section . As shown in Figure \ref{fig: results}(a)(b), AutoConfigure achieves 10-30\% higher accuracy with a similar amount of resources, or achieve a similar accuracy with only 50-80\% of the resources on a single-camera dataset. As shown in Figure \ref{fig: results}(c), the gap between AutoConfigure and static configuration is larger than Figure \ref{fig: results}(a)(b), indicating that AutoConfigure has a better improvement on the multi-camera situation. AutoConfigure achieves 25-35\% higher accuracy with a similar amount of resources, or achieve higher accuracy with only 75-85\% of the resources on Multi-Camera Dataset. In a word, AutoConfigure can improve 10-35\% higher accuracy or save 50-85\% resource consumption.

\subsubsection{Different AutoConfigure Solutions}
\label{subsec: different sulutions}
In the training phase, when using different balance factors $\beta$ in the reward function, we would obtain different agents (different automatic configuration strategies). In general, the $\beta$ is bigger, indicating the accuracy is more important relatively, and the agent would choose a more expensive configuration. In our experiment, we set $\beta$ is 0.2,0.3,...,0.9, and the results of different AutoConfigure solutions on Multi-Camera Dataset are listed in Table \ref{tab: different sulutions}.

\begin{table}[!t]
	\centering
	%     \begin{tabular}{lll}
	\resizebox{0.4\textwidth}{!}{
		\begin{tabular}{ccc}
			\toprule
			balance factor $\beta$ & Avg GPU time per frame (second) & Avg F1 score  \\ \midrule
			0.2          & 0.01384  &  0.64307            \\
			0.3          & 0.03314  &  0.72008            \\
			0.4          & 0.04921  &  0.78920            \\
			0.5          & 0.05203  &  0.79096            \\
			0.6          & 0.08479  &  0.80056            \\
			0.7          & 0.17570  &  0.87731            \\
			0.8          & 0.26511  &  0.93262            \\
			0.9          & 0.30937  &  0.96537           \\
			\bottomrule
	\end{tabular}}
	\caption{Resource consumption and F1 accuracy for different AutoConfigure solutions}
	\label{tab: different sulutions}
	% \vspace{-0.5cm}
\end{table}

Table \ref{tab: different sulutions} shows that when the $\beta$ increases, the resource consumption and the accuracy of the corresponding solution both would increase, indicating the AutoConfigure solutions of big $\beta$ would choose the more expensive configuration to inference. We can leverage this to train proper configuration strategy for different service demands, for example, using big $\beta$ for high-accuracy demand services and using small $\beta$ for low-accuracy demand services.

\subsubsection{Profile Cost}
\label{subsec: profile cost}
Comparing to the static solution that profiles configurations once, in our solution, the video
chunk is passed to the AutoConfigure firstly to estimate the configuration. Running this RL agent brings profile cost (extra resource consumption) to the whole system. In this section, we evaluate this profile cost. In the inference phase, we divide the video into $T$-second intervals as video chunks and use AutoConfigure to choose the proper configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds. We use T = 4 and t = 1 for our experiments. The profile cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions. In our test, the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored. We compute the ratio by dividing profile time into total inference time, which is equals the frame number multiply the average time per frame. The profile time is about 0.1-1\% of the overall video analytics resource consumption. The concrete ratio depends on the concrete AutoConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}.

@@

### 2020-12-02 paper/sections/introduction.tex
first draft

\section{Introduction}
\textcolor{note}{this section is too long}

@@

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is a video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}. Different configurations directly affect accuracy and resource consumption. Using a fixed static high configuration can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a low configuration will result in a significant reduction in accuracy.

%Apparently, choosing different configurations will affect resource consumption and accuracy. When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

\begin{figure*}[!t]
	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
	%	\vspace{0.2cm}
	\caption{Framework of AutoConfigure architecture}
	\label{fig: framework}
\end{figure*}

%We use~\autoref{fig2} to support that, the data in this figure come from a real road. It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the decrease of accuracy is partly acceptable.

@@

The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}. Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold. On the one hand, if one only profiles the processing pipeline to choose the best configuration \emph{once}, the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by picking a cheap configuration). On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs.

%The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations, but the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.

For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem, which is challenging to be solved by rules. An automatic approach is needed, one that is able to learn from video contexts, to decide what is the best configuration for the current video context. The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem. In our solution, we tackle the following design challenges.

%Also, one is not provided the well-labeled data on which configuration should be used in which time of the video, meaning this is an unsupervised learning task.

\begin{itemize}	
\item \emph{The best configuration for a video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

@@

\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized in an online manner, and the solution has to learn from the video contexts automatically. 
\end{itemize}

To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way. A brief framework of AutoConfigure is shown in Figure~\ref{fig: framework}. \textcolor{note}{some description?} The main contributions of this paper are summarized as follows.

\begin{itemize}	
\item We design an interactive training environment that can be applied to different video analytics applications. We propose an Deep Q-learning Network-based \cite{DQN} agent to pick the best configuration for video analytics. Also, we define the elements of the RL-based approach, such as actions, states and rewards, to adapt the configuration to current video context.

@@

\item AutoConfigure can achieve 20-30\% higher accuracy with the
same amount of resources, or achieve the same accuracy
with only 50-70\% of the resources. Furthermore, AutoConfigure proves to be more efficient than existing baselines by creating an overhead of less than xx\%\textcolor{note}{(To be tested)} to the overall video analytics services.
\end{itemize}

>>>>

\section{Introduction}

@@

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the inference accuracy. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}. Different configurations directly affect accuracy and resource consumption. Using a fixed static high configuration can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a low configuration will result in a significant reduction in accuracy.

%Apparently, choosing different configurations will affect resource consumption and accuracy. When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. When the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a considerable reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve satisfactory accuracy. And in the case of highway video analytics, the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout the whole video. This can significantly reduce resource consumption but does not affect the accuracy of video analytics.

%\begin{figure*}[!t]
%	\centerline{\includegraphics[width=0.9\linewidth]{figures/framework.pdf}}
%	%	\vspace{0.2cm}
%	\caption{Framework of AutoConfigure architecture}
%	\label{fig: framework}
%\end{figure*}

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/static_framework.pdf}}
		\begin{center}
			{(a) Static configuration solution: fixed configuration for video analytics services}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.8\linewidth]{figures/auto_framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AutoConfigure solution: context-driven automatic configuration framework}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
	\label{fig: framework}
\end{figure*}

%We use~\autoref{fig2} to support that, the data in this figure come from a real road. It can be found that with the decrease of frame rate, the resource consumption can be significantly reduced, but the reduction of accuracy is partly acceptable.

@@

The \emph{best} configuration for a video analytics services also varies over time, often at a timescale of minutes or even seconds \cite{jiang2018chameleon}. Hence, our goal is to find a range of ``most appropriate'' configurations that takes up the minimum amount of computing resources and is accurate to the desired threshold. On the one hand, like figure~\ref{fig: framework}(a), if one uses a static configuration solution (i.e.only profiles the processing pipeline to choose the best configuration \emph{once}), the application would either waste resources (by picking an expensive configuration) or sacrifice accuracy (by selecting a cheap configuration). On the other hand, if one periodically profiles the processing pipeline to find an optimal resource-accuracy \emph{tradeoff} by exhaustive all configurations, it would be prohibitively expensive since the configuration space is extremely large, and thousands of configurations can be combined with just a few knobs. To tackle these challenges, we propose an automatic configuration approach, AutoConfigure, and the brief framework is shown in Figure~\ref{fig: framework}(b).

%The most intuitive way to solve this problem is to find the best solution by exhaustive all configurations. Still, the number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs, so exhaustive configuration is a highly unrealistic approach.

For a video analytics application, choosing the ``most appropriate'' configuration is a complicated decision-making problem that is challenging to solve by rules. An automatic approach is needed to learn from video contexts to decide the best configuration for the current video context. The reinforcement learning method is an excellent way to solve this unsupervised complex-environmental problem. In our solution, we tackle the following design challenges.

%Also, one is not provided the well-labeled data on which configuration should be used at which time of the video, meaning this is an unsupervised learning task.

\begin{itemize}	
	\item \emph{The best configuration for video analytics services changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly require a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

@@

	\item \emph{Lack of well-labeled training data.} In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized online, and the solution has to automatically learn from the video contexts. 
\end{itemize}

To address the above challenges, we present a context-driven automatic configuration framework based on reinforcement learning, called AutoConfigure, which can dynamically select the ``most appropriate'' configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a very low-cost way. The main contributions of this paper are summarized as follows.

\begin{itemize}	
	\item We design an interactive training environment that can be applied to different video analytics applications. We propose a Deep Q-learning Network-based \cite{DQN} agent to pick the best video analytics configuration. Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to adapt the configuration to the current video context.

@@

	\item AutoConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 50-85\% of the resources. AutoConfigure proves to be more efficient than static solutions and only creates an overhead of 0.1-1\% to the overall video analytics services.
\end{itemize}
